Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-04-11 ms.tex
addressing more comments

\subsection{Compact Sources}
\label{sec:ptsrc}
%start by mentioning that SFD removed compact sources (outside of b +/- 5)
After subtracting the SMICA CMB model, we next proceeded to interpolate 
over compact sources, including both point sources and resolved galaxies. 
Removing compact sources at this stage is important as it prevents 
contamination of compact-source-free pixels in our downstream analyses which 
require smoothing of the \PLANCK~maps. SFD carefully removed point sources and 
galaxies from the \verb|i100| map everywhere outside of 
$|b|$$<$$5^{\circ}$. We do not perform any further modifications of the 
\verb|i100| map to account for compact sources. To mask compact sources in the 
\PLANCK~maps, we use the SFD compact source mask, which was originally 
constructed to mask point sources and resolved compact objects that are not 
part of the Galactic cirrus at 3000 GHz. Given our pixelization (see 
$\S$\ref{sec:pix}), 1.56\% of pixels are masked.

@@

Although we wish to isolate and model thermal emission from Galactic dust, the
\PLANCK~maps contain additional components on large angular scales. At each 
frequency, there can exist an overall, constant offset that must be subtracted 
to set the zero level of Galactic dust. Additionally, faint residuals of the 
Solar dipole remain at low frequencies. We will address these issues by
separately solving two sub-problems: first, fixing the absolute zero level 
relative to external data, and second fitting per-band relative offsets 
and low order corrections by correlating the \PLANCK~bands against one another.
%this last sentence needs lots of work

@@

>>>>

\subsection{Compact Sources}
\label{sec:ptsrc}
%start by mentioning that SFD removed compact sources (outside of b +/- 5)
After subtracting the SMICA CMB model, we interpolate over compact sources, 
including both point sources and resolved galaxies. Removing compact sources at
this stage is important as it prevents contamination of compact-source-free 
pixels in our downstream analyses which require smoothing of the \PLANCK~maps. 
SFD carefully removed point sources and galaxies from the \verb|i100| map 
everywhere outside of $|b|$$<$$5^{\circ}$. We do not perform any further 
modifications of the \verb|i100| map to account for compact sources. To mask 
compact sources in the \PLANCK~maps, we use the SFD compact source mask, which 
was originally constructed to mask point sources and resolved compact objects 
that are not part of the Galactic cirrus at 3000 GHz. Given our pixelization 
(see $\S$\ref{sec:pix}), 1.56\% of pixels are masked.

@@

Although we wish to isolate and model thermal emission from Galactic dust, the
\PLANCK~maps contain additional components on large angular scales. At each 
frequency, there can exist an overall, constant offset that must be subtracted 
to set the zero level of Galactic dust by removing the mean cosmic IR 
background, as well as any instrumental offset. Additionally, faint residuals 
of the Solar dipole remain at low frequencies. We will address these issues by 
separately solving two sub-problems: first, fixing the absolute zero level 
relative to external data, and second fitting per-band relative offsets and low
order corrections by correlating the \PLANCK~bands against one another.
%this last sentence needs lots of work

@@

% maybe state approximately what 0.37 MJy/sr at 857 GHz equates to in EBV
% --> did a quick calculation and it's only ~0.0118 mags ... thought it
%     would be more ??
